---
title: "Insurance Register"
imgSrc: "../../assets/images/archive.webp"
imgAlt: "Facade of Greek Parliament"
description: "A list of (re)insurance companies in Greece and insurance sub-sectors"
periodText: "PERIOD"
period: "2022"
recordsText: "RECORDS"
records: "973"
languageText: "LANGUAGE"
languageAns: "Greek / English"
exploreDatasetText: "Explore dataset"
toc: true
toc-location: left
comments: false
lang: en
order: 3
---

::: {.text-center .lh-lg}
<i class="bi bi-code-slash"></i> `Programming Language`: R <br>
<i class="bi bi-code-slash"></i> `Software`: rvest <br>
<i class="bi bi-database"></i> `Data Source`: [Bank of Greece](https://www.bankofgreece.gr/) <br>
<i class="bi bi-list-ol"></i> `# of observations - rows`: 973 <br>
<i class="bi bi-list-ol"></i> `# of variables - columns`: 9 <br>
<i class="bi bi-translate"></i> `Languages`:  🇬🇧  / 🇬🇷 <br>
<i class="bi bi-activity"></i> `Frequency `: Μη επαναλαμβανόμενο
:::


:::{.d-flex .flex-column .flex-sm-row .justify-content-center .gap-3 .align-items-center .justify-content-center .p-2}
```{=html}
<div><a href="https://github.com/stesiam/insuranceRegister/releases/tag/v1.0.0" class="btn btn-primary btn-md"><i class="bi bi-globe"></i> Data</a></div>
<div><a href="https://github.com/stesiam/insuranceRegister" class="btn btn-primary btn-md"><i class="bi bi-github"></i> Repository</a></div>
```
:::

## Dataset variables


```{r}
#| echo: false
#| message: false
library(dplyr)
library(readr)
library(gt)

source("../../../posts/utils.R")
url = "https://github.com/stesiam/insuranceRegister/releases/download/v1.0.0/GRins.csv"
```

| Variable | Variable Type | Description |
|:---------|:-----|:------------|
| `name` | qualitative | Name of insurance company |
| `type` | qualitative | Type of Insurance Company |
| `category` | qualitative | Insurance coverage category (life, non-life, mixed) |
| `status` | qualitative | Insurance company status (Active / Ceased / Licence revoked / Under liquidation) |
| `auth_country` | qualitative | Authorization Country |
| `country_of_auth` | qualitative | Country of autharisation |
| `website_url` | qualitative | Website of insurance company |
| `link` | qualitative | Company profile on Bank of Greece register  |
| `address` | qualitative | Address of company |

: {.table .table-sm .table-borderless}


## Preview dataset

```{r}
#| echo: false
#| message: false
readr::read_csv(url) %>%
  mutate(across(where(is.character), ~ifelse(nchar(.) > 80, paste0(substr(., 1, 80), "…"), .))) %>%
  gt_custom(use_labels = FALSE, head_max = 20)
```


## Download data files

If you are unsure which format to choose, `CSV` is the most common format and is easier to analyze with a wide range of software tools.

| File format | Download link |
|:---------|:-----|
| `.csv` | [Download csv](https://github.com/stesiam/insuranceRegister/releases/download/v1.0.0/GRins.csv) |
