---
title: "Franchises in Greece"
imgSrc: "../../assets/images/chairs.webp"
imgAlt: "Modern minimalist conference room with a long white table, grey chairs, a wall-mounted TV"
description: "A list of companies that offer franchise plans in Greece with respected required amount of investment, royalties and other fees"
periodText: "PERIOD"
period: "1981-2020"
recordsText: "RECORDS"
records: "4 503"
languageText: "LANGUAGE"
languageAns: "Greek / English"
exploreDatasetText: "Explore dataset"
toc: true
toc-location: left
comments: false
lang: en
order: 4
---

::: {.text-center .lh-lg}
<i class="bi bi-code-slash"></i> `Programming Language`: R <br>
<i class="bi bi-code-slash"></i> `Software`: rvest <br>
<i class="bi bi-database"></i> `Data Source`: [Franchise Portal GR](https://franchiseportal.gr/) <br>
<i class="bi bi-list-ol"></i> `# of observations - rows`: 421 <br>
<i class="bi bi-list-ol"></i> `# of variables - columns`: 23 <br>
<i class="bi bi-translate"></i> `Languages`:  🇬🇧  / 🇬🇷 <br>
<i class="bi bi-activity"></i> `Frequency `: Non-repeating
:::

:::{.d-flex .flex-column .flex-sm-row .justify-content-center .gap-3 .align-items-center .justify-content-center .p-2}
```{=html}
<div><a href="https://github.com/stesiam/greek-franchise-tracker/releases/tag/v1.0.0" class="btn btn-primary btn-md"><i class="bi bi-globe"></i> Δεδομένα</a></div>
<div><a href="https://github.com/stesiam/greek-franchise-tracker" class="btn btn-primary btn-md"><i class="bi bi-github"></i> Αποθετήριο</a></div>
```
:::

## Dataset variables


```{r}
#| echo: false
#| message: false
library(dplyr)
library(readr)
library(gt)

source("../../../posts/utils.R")
url = "https://github.com/stesiam/greek-franchise-tracker/releases/download/v1.0.0/franchises_clean.csv"
```


| Variable | Variable Type | Description |
|:---------|:-----|:------------|
| `name` | qualitative | Franchise name |
| `category` | qualitative | Franchise business category |
| `img` | qualitative | Franchise logo |
| `link` | qualitative | Franchise profile page on the source website |
| `min_investment` | quantitative | Minimum required investment amount |
| `store_size_min` | quantitative | Minimum store size (in sq.m.) |
| `store_size_max` | quantitative | Maximum store size (in sq.m.) |
| `entry_fee` | quantitative | One-time franchise entry fee |
| `royalties` | qualitative | Royalty fees |
| `branches_corp` | quantitative | Corporate branches |
| `branches_franch` | quantitative | Individual franchisee stores |
| `total_branch` | quantitative | Total number of stores |
| `start_activity` | quantitative | Start of business activity |
| `start_franchise` | quantitative | Start of franchise operations |
| `origin` | qualitative | Country of origin |
| `experience` | qualitative | Is prior experience required? |
| `self_employment` | qualitative | Is self-employment required? |
| `franchise_agreement` | qualitative | Franchise agreement duration |
| `headquarters` | qualitative | Company headquarters |
| `company_name` | qualitative | Company legal name |
| `phone` | qualitative | Contact phone number |
| `fax` | qualitative | Contact fax number |
| `website` | qualitative | Company website |

: {.table .table-sm .table-borderless .table-responsive}


## Preview dataset


```{r}
#| echo: false
#| message: false
readr::read_csv(url) %>%
  mutate(across(where(is.character), ~ifelse(nchar(.) > 80, paste0(substr(., 1, 30), "…"), .))) %>%
  gt_custom(use_labels = FALSE, head_max = 20)
```



## Download data files

If you are unsure which format to choose, `csv` is the most common format and is easier to analyze with a wide range of software tools.


| File format | Download link |
|:---------|:-----|
| `.csv` | [Download csv](https://github.com/stesiam/greek-franchise-tracker/releases/download/v1.0.0/franchises_clean.csv) |

