---
title: "Job Postings"
imgSrc: "../../assets/images/jobposts.webp"
imgAlt: "Facade of Greek Parliament"
description: "A collection of 5000+ job postings on February, 2025 extracted from xe.gr "
periodText: "PERIOD"
period: "Jan - Feb 2025"
recordsText: "RECORDS"
records: "5 093"
languageText: "LANGUAGE"
languageAns: "Greek / English"
exploreDatasetText: "Explore dataset"
toc: true
toc-location: left
comments: false
lang: en
order: 1
---


::: {.text-center .lh-lg}
<i class="bi bi-code-slash"></i> `Programming Language`: R <br>
<i class="bi bi-code-slash"></i> `Software`: rvest <br>
<i class="bi bi-database"></i> `Data Source`: [xe.gr](https://www.xe.gr/) <br>
<i class="bi bi-list-ol"></i> `# of observations - rows`: 5093 <br>
<i class="bi bi-list-ol"></i> `# of variables - columns`: 9 <br>
<i class="bi bi-translate"></i> `Languages`:  🇬🇧  / 🇬🇷 <br>
<i class="bi bi-activity"></i> `Frequency `: Non-repeating
:::


:::{.d-flex .flex-column .flex-sm-row .justify-content-center .gap-3 .align-items-center .justify-content-center .p-2}
```{=html}
<div><a href="https://github.com/stesiam/scraping-job-postings-xe/releases/tag/v1.2" class="btn btn-primary btn-md"><i class="bi bi-database"></i> Data</a></div>
<div><a href="https://github.com/stesiam/scraping-job-postings-xe" class="btn btn-primary btn-md"><i class="bi bi-github"></i> Repository</a></div>
```
:::

## Dataset Variables

The database consists of two tables in total. The first contains the scraped job listing data, while since version 1.3 a second table has been added, which classifies each listing according to various types of discrimination, leveraging the `{ellmer}` package and a large language model.

The scraped data contains the following variables:

```{r}
#| echo: false
#| message: false
library(dplyr)
library(readr)
library(gt)

source("../../../posts/utils.R")
url = "https://github.com/stesiam/scraping-job-postings-xe/releases/download/v1.2/job-posts.csv"
```

| Variable | Type | Description |
|:---------|:-----|:------------|
| `spc` | qualitative | Occupation |
| `type` | qualitative | Employment terms |
| `wage` | mixed | Salary / Salary range |
| `loc` | qualitative | Location |
| `exp` | qualitative (ordinal) | Required work experience |
| `descr` | qualitative | Job listing text |
| `p_date` | qualitative | Publication date |
| `link` | qualitative | Listing URL (no longer verifiable) |

: Job listings dataset variables : {.table .table-sm .table-borderless .table-responsive}



While the job listing assessment table:

| Variable | Type | Description |
|:---------|:-----|:------------|
| `has_age_discrimination` | binary | Was age discrimination detected? |
| `has_gender_discrimination` | binary | Was gender discrimination detected? |
| `has_appearance_discrimination` | binary | Was appearance discrimination detected? |
| `is_policy_related` | binary | Discrimination attributable to employment programs |
| `has_racial_discrimination` | binary | Was racial discrimination detected? |
| `reasoning` | qualitative | Explanation of classifications for each observation / listing |

: Assessment dataset variables : {.table .table-sm .table-borderless .table-responsive}



## Preview dataset

```{r}
#| echo: false
#| message: false
readr::read_csv(url) %>%
  mutate(across(where(is.character), ~ifelse(nchar(.) > 80, paste0(substr(., 1, 25), "…"), .))) %>%
  gt_custom(use_labels = FALSE, head_max = 10)
```


## Download data files

If you are unsure which format to choose, `CSV` is the most common format and is easier to analyze with a wide range of software tools.

For the file containing the job postings (`job-posts`):

| File format | Download link |
|:---------|:-----|
| `.csv` | [Λήψη csv](https://github.com/stesiam/scraping-job-postings-xe/releases/download/v1.3/job-posts.csv) |
| `.rds` |  [Λήψη rds](https://github.com/stesiam/scraping-job-postings-xe/releases/download/v1.3/job-posts.rds) |
| `.parquet` |  [Λήψη parquet](https://github.com/stesiam/scraping-job-postings-xe/releases/download/v1.3/job-posts.parquet) | 
| `.feather` |  [Λήψη feather](https://github.com/stesiam/scraping-job-postings-xe/releases/download/v1.3/job-posts.feather) | 
| `.sqlite` |  [Λήψη sqlite](https://github.com/stesiam/scraping-job-postings-xe/releases/download/v1.3/job-posts.sqlite) |

The classification dataset (`llm-classification`) is available only in CSV format:

| File format | Download link |
|:---------|:-----|
| `.csv` | [Λήψη csv](https://github.com/stesiam/scraping-job-postings-xe/releases/download/v1.3/llm_classification.csv) |
