---
title: "Elected MPs"
imgSrc: "../../assets/images/houses-of-parliament.jpg"
imgAlt: "Facade of Greek Parliament"
description: "MPs elected on Greek Parliament (1974 - 2023A)"
periodText: "PERIOD"
period: "1974-2023"
recordsText: "RECORDS"
records: "5 704"
languageText: "LANGUAGE"
languageAns: "Greek / English"
exploreDatasetText: "Explore dataset"
toc: true
toc-location: left
comments: false
lang: en
order: 2
---

::: {.text-center .lh-lg}
<i class="bi bi-code-slash"></i> `Programming Language`: R <br>
<i class="bi bi-code-slash"></i> `Software`: rvest <br>
<i class="bi bi-database"></i> `Data Source`: [Hellenic Parliament](https://www.hellenicparliament.gr/en/) <br>
<i class="bi bi-list-ol"></i> `# of observations - rows`: 5704 <br>
<i class="bi bi-list-ol"></i> `# of variables - columns`: 5 <br>
<i class="bi bi-translate"></i> `Languages`:  🇬🇧  / 🇬🇷 <br>
<i class="bi bi-activity"></i> `Frequency `: Non-repeating
:::


:::{.d-flex .flex-column .flex-sm-row .justify-content-center .gap-3 .align-items-center .justify-content-center .p-2}
```{=html}
<div><a href="https://github.com/stesiam/scrape-greek-parl-members-26/releases/tag/v1.1.0" class="btn btn-primary btn-md"><i class="bi bi-database"></i> Data</a></div>
<div><a href="https://github.com/stesiam/scrape-greek-parl-members-26" class="btn btn-primary btn-md"><i class="bi bi-github"></i> Repository</a></div>
```
:::

## Dataset variables


```{r}
#| echo: false
#| message: false
library(dplyr)
library(readr)
library(gt)

source("../../../posts/utils.R")
url = "https://github.com/stesiam/scrape-greek-parl-members-26/releases/download/v1.1.0/parlMembers-eng.csv"
```

| Variable | Type | Description |
|:---------|:-----|:------------|
| `name` | qualitative | Full name of the parliament member |
| `party` | qualitative | Political party affiliation |
| `region` | qualitative | Electoral region they represent |
| `period_names` | qualitative (ordinal) | Period name (number of plenum)  |
| `dates` | qualitative (ordinal) | Link to their official parliament profile |
| `gender` | qualitative | Εκτιμώμενο φύλο του αντίστοιχου βουλευτή με βάση το όνομά του |

: {.table .table-sm .table-borderless .table-responsive}


## Preview dataset

```{r}
#| echo: false
#| message: false
readr::read_csv(url) %>%
  mutate(across(where(is.character), ~ifelse(nchar(.) > 80, paste0(substr(., 1, 80), "…"), .))) %>%
  gt_custom(use_labels = FALSE, head_max = 20)
```


## Download data files

If you are unsure which format to choose, `CSV` is the most common format and is easier to analyze with a wide range of software tools.

| File format | Download link |
|:---------|:-----|
| `.csv` | [Download csv](https://github.com/stesiam/scrape-greek-parl-members-26/releases/download/v1.1.0/parlMembers-eng.csv) |
| `.rds` |  [Download rds](https://github.com/stesiam/scrape-greek-parl-members-26/releases/download/v1.1.0/parlMembers-eng.rds) |
| `.json` |  [Download json](https://github.com/stesiam/scrape-greek-parl-members-26/releases/download/v1.1.0/parlMembers-eng.json) | 
| `.parquet` |  [Download parquet](https://github.com/stesiam/scrape-greek-parl-members-26/releases/download/v1.1.0/parlMembers-eng.parquet) | 
| `.feather` |  [Download feather](https://github.com/stesiam/scrape-greek-parl-members-26/releases/download/v1.1.0/parlMembers-eng.feather) | 
| `.sqlite` |  [Download sqlite](https://github.com/stesiam/scrape-greek-parl-members-26/releases/download/v1.1.0/parlMembers-eng.sqlite) | 